%!TEX Ts-program = xelatex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Alex} \headerlastnamestyle{Koen} \\
	\vspace{2mm}
	{\faEnvelope\ arw.koen@gmail.com} | {\faGlobe\ alexkoen.com} | {\faMobile\ (778) 834-7794} | {\faMapMarker\ 1176 Brackenell Cres, North Vancouver, BC}
\end{center}

\cvsection{Summary}

A hard-working and dedicated first year engineering student at the University of British Columbia intending to pursue a degree in Engineering Physics. I have a proven ability to communicate with people of all ages, exemplified by my position as Vice-Chair of Communications for the youth council of Minister Jonathan Wilkinson.

% \cvsection{Skills}
% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{Public speaking} \\
%     Fluent in both English and French and has won several awards for public speaking.
%   \end{minipage}\hfill
% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{Teamwork} \\
%     Extensive experience working as a team to achieve a common goal.
% \end{minipage}\hfill
% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{Communication} \\
%     Has proven communication skills and an ability to communicate effectively with anyone.
% \end{minipage}

% \vspace{10pt}

% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{First Aid} \\
%     Certified First Responder with over four years of volunteer experience. 
%   \end{minipage}\hfill
% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{Skiing} \\
%     Able to ski all terrain with confidence and strong technique.
% \end{minipage}\hfill
% \begin{minipage}[t]{.25\linewidth}
%     \entrytitlestyle{Linux} \\
%     Experience as a Linux administrator and proficient with vim, git, and bash. 
% \end{minipage}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Work \& Volunteer Experience}
\cventry
  {Medical Applications in Software Technology - UBC BEST}
  {Head designer and software developer}
  {Vancouver, BC}
  {Sept. 2019 - Present}
  {\begin{cvitems}
      \item {Worked with Vancouver General Hospital and the Vancouver Radiology Institute to develop a web and mobile application for paramedics and healthcare professionals.}
  \end{cvitems}}


  \cventry
  {The Honourable Jonathan Wilkinson's Youth Council}
  {Vice-Chair of Communications \& Web Designer}
  {North Vancouver, BC}
  {Oct. 2018 - Jun. 2019}
  {\begin{cvitems}
      \item {Elected as Vice-Chair of Communications after displaying a dedication to the council and an exemplary ability to communicate.}
      \item {Interfaced directly with the Minister and the media to present projects to the public.}
      \item {Built a responsive website from scratch to showcase our event, \textit{Youth Visioning Our City's Future,} to the general public.}
  \end{cvitems}}
  \cventry
  {Handsworth Theatre Program}
  {Head Writer}
  {North Vancouver, BC}
  {Jun. 2018 - Apr 2019}
  {\begin{cvitems}
      \item {Co-wrote an original play, \textit{Cast Iron Lily,} for over 200 cast members and which raised over \$50,000 in ticket sales.}
      \item {Worked closely with four other head writers to both write and lead the other students during the production.}
    \end{cvitems}}
\begin{cventries}
  \cventry
  {Grouse Mountain Resorts}
  {Ski Instructor}
  {North Vancouver, BC}
  {Dec. 2016 – Mar. 2019 (Seasonal)}
  {\begin{cvitems}
    \item {Worked with clients of all ages to provide them with a positive and memorable  experience.}
    \item {Developed ability to educate clients and gained a higher level of responsibility within the department.}
    \end{cvitems}}
  \cventry
  {21st Capilano Medical Venturers \& Handsworth First Responders Team}
  {First Responder Volunteer}
  {North Vancouver, BC}
  {Summer 2015 – Present}
  {\begin{cvitems}
      \item {Elected as president of the Handsworth First Responders Team.}
    \item {Helped others by working as a team to provide First Aid to those in need.}
    \end{cvitems}}
  \cventry
  {Pacific Scout Jamboree}
  {Roving Security Unit Medic}
  {Sooke, BC}
  {Jul. 2015}
  {\begin{cvitems}
      \item {Spent two weeks volunteering as a medic for a 100+ member medical team.}
  \end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
  \cventry
  {University of British Columbia}
  {First Year Engineering Student}
  {Vancouver, BC}
  {Present}
  {\begin{cvitems}
     \item Current GPA: 92\% 
    \end{cvitems}}
  \cventry
  {Handsworth Secondary}
  {Graduate with Honours}
  {North Vancouver, BC}
  {Jul. 2019}
  {}
  \cventry
  {Level 2 Ski Instructor with Children\textquotesingle{}s Module}
  {CSIA Level 2}
  {}
  {April 2017}
  {}
  \cventry
  {Certified First Responder by the Canadian Red Cross}
  {First Responder}
  {}
  {February 2016}
  {}
\end{cventries}

\cvsection{Awards}
\begin{cvhonors}
  \cvhonor
  {BC Achievement Scholarship}
  {Top 8,000 graduating students in the province}
  {}
  {Sept. 2019}

  \cvhonor
  {Ray Noel Citizenship Award}
  {Scholarship recipient}
  {}
  {June 2019}

  \cvhonor
  {Distinguished Graduate Award}
  {Top 10\% of graduating sudents}
  {}
  {May 2019}

  \cvhonor
  {2018 Provincial Councours d'Art Oratoire Winner}
  {Grade 11 French Immersion category}
  {}
  {May 2018}

\end{cvhonors}

\cvsection{References}
References available upon request.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% End:
